---
title: "Beer and BAC Regression Analysis"
author: "Shrawani Pradhan & Taha Mohiuddin"
format: html
editor: visual
---

## Introduction

In this project, we analyze the relationship between the number of beers consumed and the resulting Blood Alcohol Content (BAC). Using simple linear regression, we estimate how BAC changes based on beer intake. All computations are done using Base R functions we implemented ourselves.

## Loading Dataset

```{r}
bac <- read.csv("~/Downloads/bac.csv") # need to paste your filepath here
bac
```

You can add options to executable code like this

```{r}
ref.model <- lm(bac ~ beers + 1, data = bac)
ref.model
```

```{r}
ref.summary <- summary(ref.model)
ref.summary
```

## Custom Functions

```{r}
source("~/Downloads/SimpleRegression.R")
```

## Run Simple Regression

```{r}
x <- bac$beers
y <- bac$bac

our.model <- simple_regression(y, x)
```

## Summary Output

```{r}
display_report(our.model)
```
## Brief Description of data
This dataset bac.csv contains information regarding how the number of beers consumed affects someones BAC.
The rows of data are the participants information
What we are attempting to discover is the relationship between number of beers someone consumes and their BAC

## Predictive and explanatory power
The R squared value proves that the BAC is directly correlated to the number of beers consumed 
Adjusted R squared value is similar to R^2 value which suggests the model does not overfit. These 2 metrics prove the model is explanatory.

## Conclusion
This project used a simple linear regression model to explore the relationship between BAC and number of beers consumed by someone.
